The Anatomy of a Temporal Summarization System

### 2015-01-27 problemdefinition.tex
Added event types to problemdefinition

\fdcomment{include description of nuggets here.}

>>>>

We address  disaster types such as terrorism and mass shootings (e.g.,
the 2012 shooting in Aurora, Col.), natural disasters (e.g., Hurricane Sandy),
accidents (e.g., the 2012 Pakistan garment factory fire), astronomical
disasters (e.g,. the Chelyabinsk comet in Russia), and social activism (e.g.,
the Arab spring).
\kmcomment{This was as best as I could do on this. These are the example
  categories from the wikipedia page. However you refer in the language model
  description to the event type earthquake which is more specific. Also, in the
  TREC data you refer to event types that are specified in the metadata. So I'm
  wondering how many different categories you have and where they come from.}

\fdcomment{include description of nuggets here.}
\kmcomment{We should jointly discuss what goes in data and what goes in problem
  definition. I have moved event types here because I think knowing how many
  types and examples of them would be helpful upfront. I think where nuggets
  and wikipedia pages go is questionable.}
